paper

### 2024-09-28 inst/extdata/paperdata/paper.qmd
.

# Set metadata and formula for LimROTS analysis
meta.info <- names(soma@colData@listData)
B <- 1000  # Number of bootstrap samples
K <- dim(soma)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "group_comp"
formula.str <- "~ 0 + group_comp + gender + AGE + CNO"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

@@

saveRDS(limrots.result, "D:/LimROTS/inst/extdata/paperdata/Soma.noPCs.LimROTS.rds")

@@

```{r}
set.seed(1234, kind = "default")

soma0.5 <- soma[, sample(1:524, 262) , drop = FALSE]

@@

# Set metadata and formula for LimROTS analysis
meta.info <- names(soma0.5@colData@listData)
B <- 1000  # Number of bootstrap samples
K <- dim(soma0.5)[1]/2  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "group_comp"
formula.str <- "~ 0 + group_comp + gender + AGE + CNO"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

soma0.5 <- LimROTS(data.exp = soma0.5, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE, progress = TRUE, seed.cl = 1234)

saveRDS(soma0.5, "../paperdata/Soma0.5.noPCs.LimROTS.rds")

@@

```{r}
soma0.5 <- readRDS("Soma0.5.noPCs.LimROTS.rds")

plot(soma0.5$q_values)
hist(soma0.5$q_values)
hist(soma0.5$q_values$qvalues)
hist(soma0.5$FDR)

summary(soma0.5$q_values)
```

@@

length(intersect(soma.sig, soma0.5.sig))
```

@@

soma0.5 <- soma[, sample(1:524, 262) , drop = FALSE]

@@

keep_samples <- colData(soma)$CNO != 12
soma <- soma[, keep_samples]

>>>>

# Set metadata and formula for LimROTS analysis
meta.info <- names(soma@colData@listData)[1:4]
B <- 1000  # Number of bootstrap samples
K <- dim(soma)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "group_comp"
formula.str <- "~ 0 + group_comp + gender + AGE + CNO"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

@@

saveRDS(limrots.result, "../paperdata/Soma.noPCs.LimROTS.rds")

@@

```{r}
library(LimROTS)
library(parallel)

set.seed(1234, kind = "default")

data("proteogenomicPD")

group1 <- sample(which(colData(soma)$group_comp == 1), length(which(colData(soma)$group_comp == 1))/1.8 )

group2 <- sample(which(colData(soma)$group_comp == 2), length(which(colData(soma)$group_comp == 2))/1.8 )

soma0.5 <- soma[, c(group1, group2) , drop = FALSE]

@@

colData(soma0.5)$CNO <- droplevels(colData(soma0.5)$CNO)

soma0.5@assays@data@listData[["norm"]] <- preprocessCore::normalize.quantiles(as.matrix(soma0.5@assays@data@listData[["norm"]]))

# Set metadata and formula for LimROTS analysis
meta.info <- names(soma0.5@colData@listData)[1:3]
B <- 1000  # Number of bootstrap samples
K <- dim(soma0.5)[1]/4 # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "group_comp"
formula.str <- "~ 0 + group_comp + gender + AGE"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

trace(LimROTS, edit = T)

soma0.5.result <- LimROTS(data.exp = soma0.5, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE, progress = TRUE, seed.cl = 1234)

saveRDS(soma0.5.result, "../paperdata/Soma0.5.noPCs.LimROTS.rds")

@@

```{r}
soma0.5.result <- readRDS("Soma0.5.noPCs.LimROTS.rds")

plot(soma0.5.result$q_values)
hist(soma0.5.result$q_values)
hist(soma0.5.result$q_values$qvalues)
hist(soma0.5.result$FDR)

summary(soma0.5.result$q_values)
```

@@

length(intersect(soma.limrots, soma0.5.limrots))
```

@@

set.seed(1234, kind = "default")

@@

data("proteogenomicPD")

keep_samples <- colData(soma)$CNO %in% names(which(table(colData(soma0.5)$soma) <= 2))
soma <- soma[, !keep_samples]

colData(soma0.5)$CNO <- droplevels(colData(soma0.5)$CNO)
